\bf Classification and Regression on Random Dot Product Graphs

### 2024-09-19 draft.Rmd
minor changes

angle.reg.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(mse.theta = mean(mse),
                   se.theta = sd(mse) / sqrt(dplyr::n()) * n.sigma,
                   se.m = sd(mse.m) / sqrt(dplyr::n()) * n.sigma,
                   mse.m = mean(mse.m),
                   se.a = sd(mse.a) / sqrt(dplyr::n()) * n.sigma,
                   mse.a = mean(mse.a)) %>% 
  ggplot() + 
  theme_bw() + 
  scale_colour_brewer(palette = 'Set1') +
  labs(x = 'vertices per graph', y = 'MSE', colour = 'predictor') +
  geom_line(aes(x = n, y = mse.theta, colour = 'estimated angle')) + 
  geom_errorbar(aes(x = n, 
                    ymin = mse.theta - se.theta, 
                    ymax = mse.theta + se.theta,
                    colour = 'estimated angle'), 
                width = .1) + 
  geom_line(aes(x = n, y = mse.m, colour = 'modularity')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.m - se.m,
                    ymax = mse.m + se.m,
                    colour = 'modularity'), 
                width = .1) +

  geom_line(aes(x = n, y = mse.a, colour = 'assortativity')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.a - se.a,
                    ymax = mse.a + se.a,
                    colour = 'assortativity'), 
                width = .1) + 
  scale_x_log10(breaks = sort(n.vec))
```

```{r theta-mse, fig.width = 6, cache = FALSE, fig.cap = 'The average MSE of the estimated angles in scenario 1 over 50 simulations. The errorbars are the standard error.'}
angle.reg.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(theta.se = sd(theta.mse) / sqrt(dplyr::n()) * n.sigma,
                   theta.mse = mean(theta.mse)) %>% 
  ggplot() + 
  geom_line(aes(x = n, y = theta.mse)) + 
  geom_errorbar(aes(x = n, ymin = theta.mse - theta.se, ymax = theta.mse + theta.se),
                width = .1) + 
  labs(x = 'number of vertices', y = expression('MSE('~hat(theta)~')')) + 
  theme_bw() + 
  scale_y_log10() + 
  scale_x_log10(breaks = sort(n.vec))
```

@@

beta.reg.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(mse.beta = mean(mse),
                   se.beta = sd(mse) / sqrt(dplyr::n()) * n.sigma,
                   se.d = sd(mse.d) / sqrt(dplyr::n()) * n.sigma,
                   mse.d = mean(mse.d),
                   se.t = sd(mse.t) / sqrt(dplyr::n()) * n.sigma,
                   mse.t = mean(mse.t)) %>% 
  ggplot() + 
  geom_line(aes(x = n, y = mse.beta, colour = 'estimated beta parameters')) + 
  geom_errorbar(aes(x = n, 
                    ymin = mse.beta - se.beta, 
                    ymax = mse.beta + se.beta,
                    colour = 'estimated beta parameters'),
                width = .1) + 
  geom_line(aes(x = n, y = mse.d, colour = 'average degree')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.d - se.d,
                    ymax = mse.d + se.d,
                    colour = 'average degree'),
                width = .1) +

  geom_line(aes(x = n, y = mse.t, colour = 'transitivity')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.t - se.t,
                    ymax = mse.t + se.t,
                    colour = 'transitivity'),
                width = .1) +
  theme_bw() + 
  scale_colour_brewer(palette = 'Set1') +
  scale_x_log10(breaks = sort(n.vec)) + 
  labs(x = 'number of vertices', y = 'MSE', colour = 'predictor')
```

>>>>

angle.reg.df %>% 
  dplyr::filter(n >= 128) %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(mse.theta = mean(mse),
                   se.theta = sd(mse) / sqrt(dplyr::n()) * n.sigma,
                   se.m = sd(mse.m) / sqrt(dplyr::n()) * n.sigma,
                   mse.m = mean(mse.m),
                   se.a = sd(mse.a) / sqrt(dplyr::n()) * n.sigma,
                   mse.a = mean(mse.a)) %>% 
  ggplot() + 
  theme_bw() + 
  scale_colour_brewer(palette = 'Set1') +
  labs(x = 'vertices per graph', y = 'MSE', colour = 'predictor') +
  geom_line(aes(x = n, y = mse.theta, colour = 'estimated angle')) + 
  geom_errorbar(aes(x = n, 
                    ymin = mse.theta - se.theta, 
                    ymax = mse.theta + se.theta,
                    colour = 'estimated angle'), 
                width = .1) + 
  # geom_line(aes(x = n, y = mse.m, colour = 'modularity')) + 
  # geom_errorbar(aes(x = n,
  #                   ymin = mse.m - se.m,
  #                   ymax = mse.m + se.m,
  #                   colour = 'modularity'), 
  #               width = .1) + 
  geom_line(aes(x = n, y = mse.a, colour = 'graph statistics')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.a - se.a,
                    ymax = mse.a + se.a,
                    colour = 'graph statistics'), 
                width = .1) + 
  scale_x_log10(breaks = sort(n.vec))
```

```{r theta-mse, fig.width = 6, cache = FALSE, fig.cap = 'The average MSE of the estimated angles in scenario 1 over 50 simulations. The errorbars are the standard error.'}
angle.reg.df %>% 
  dplyr::filter(n >= 128) %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(theta.se = sd(theta.mse) / sqrt(dplyr::n()) * n.sigma,
                   theta.mse = mean(theta.mse)) %>% 
  ggplot() + 
  geom_line(aes(x = n, y = theta.mse)) + 
  geom_errorbar(aes(x = n, ymin = theta.mse - theta.se, ymax = theta.mse + theta.se),
                width = .1) + 
  labs(x = 'number of vertices', y = expression('MSE('~hat(theta)~')')) + 
  theme_bw() + 
  scale_y_log10() + 
  scale_x_log10(breaks = sort(n.vec))
```

@@

beta.reg.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(mse.beta = mean(mse),
                   se.beta = sd(mse) / sqrt(dplyr::n()) * n.sigma,
                   se.d = sd(mse.d) / sqrt(dplyr::n()) * n.sigma,
                   mse.d = mean(mse.d),
                   se.t = sd(mse.t) / sqrt(dplyr::n()) * n.sigma,
                   mse.t = mean(mse.t)) %>% 
  ggplot() + 
  geom_line(aes(x = n, y = mse.beta, colour = 'estimated beta parameters')) + 
  geom_errorbar(aes(x = n, 
                    ymin = mse.beta - se.beta, 
                    ymax = mse.beta + se.beta,
                    colour = 'estimated beta parameters'),
                width = .1) + 
  geom_line(aes(x = n, y = mse.d, colour = 'graph statistics')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.d - se.d,
                    ymax = mse.d + se.d,
                    colour = 'graph statistics'),
                width = .1) + 
  # geom_line(aes(x = n, y = mse.t, colour = 'transitivity')) + 
  # geom_errorbar(aes(x = n,
  #                   ymin = mse.t - se.t,
  #                   ymax = mse.t + se.t,
  #                   colour = 'transitivity'),
  #               width = .1) +
  theme_bw() + 
  scale_colour_brewer(palette = 'Set1') +
  scale_x_log10(breaks = sort(n.vec)) + 
  labs(x = 'number of vertices', y = 'MSE', colour = 'predictor')
```

### 2024-09-19 draft.tex
minor changes

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{notation-and-scope}{%
\subsection{Notation and Scope}\label{notation-and-scope}}

@@

\hypertarget{definitions-and-models}{%
\subsection{Definitions and Models}\label{definitions-and-models}}

@@

\hypertarget{connections-to-related-models}{%
\subsubsection{Connections to Related
Models}\label{connections-to-related-models}}

@@

\hypertarget{classification-and-regression-on-the-mlsm}{%
\subsubsection{Classification and Regression on the
MLSM}\label{classification-and-regression-on-the-mlsm}}

@@

\hypertarget{main-results}{%
\subsection{Main Results}\label{main-results}}

@@

\hypertarget{estimation-of-the-lsm-curves}{%
\subsubsection{Estimation of the LSM
Curves}\label{estimation-of-the-lsm-curves}}

@@

\hypertarget{recovery-of-the-underlying-distributions}{%
\subsubsection{Recovery of the Underlying
Distributions}\label{recovery-of-the-underlying-distributions}}

@@

\hypertarget{classification-and-regression}{%
\subsubsection{Classification and
Regression}\label{classification-and-regression}}

@@

\hypertarget{simulation-study}{%
\section{Simulation Study}\label{simulation-study}}

@@

\hypertarget{regression}{%
\subsection{Regression}\label{regression}}

@@

\hypertarget{classification}{%
\subsection{Classification}\label{classification}}

@@

\hypertarget{regression-1}{%
\subsection{Regression}\label{regression-1}}

@@

\hypertarget{applications}{%
\section{Applications}\label{applications}}

\hypertarget{drosophila-connectome}{%
\subsection{Drosophila Connectome}\label{drosophila-connectome}}

@@

\hypertarget{human-connectome-project-aging-study}{%
\subsection{Human Connectome Project Aging
Study}\label{human-connectome-project-aging-study}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

>>>>

\section{Introduction}\label{introduction}

@@

\section{Methods}\label{methods}

\subsection{Notation and Scope}\label{notation-and-scope}

@@

\subsection{Definitions and Models}\label{definitions-and-models}

@@

\subsubsection{Connections to Related
Models}\label{connections-to-related-models}

@@

\subsubsection{Classification and Regression on the
MLSM}\label{classification-and-regression-on-the-mlsm}

@@

\subsection{Main Results}\label{main-results}

@@

\subsubsection{Estimation of the LSM
Curves}\label{estimation-of-the-lsm-curves}

@@

\subsubsection{Recovery of the Underlying
Distributions}\label{recovery-of-the-underlying-distributions}

@@

\subsubsection{Classification and
Regression}\label{classification-and-regression}

@@

\section{Simulation Study}\label{simulation-study}

@@

\subsection{Regression}\label{regression}

@@

\subsection{Classification}\label{classification}

@@

\subsection{Regression}\label{regression-1}

@@

\section{Applications}\label{applications}

\subsection{Drosophila Connectome}\label{drosophila-connectome}

@@

\subsection{Human Connectome Project Aging
Study}\label{human-connectome-project-aging-study}

@@

\section{Discussion}\label{discussion}
